---
title: "Education vs Employment in 2019 CES"
author: "Justin Lee"
date: 2015-07-23T21:13:14-05:00
bibliography: "references.bib"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

# Abstract

# Introduction

We use @citetidyverse

```{r, include= FALSE}
#install cesR datasets and relevant packages
install.packages("devtools")
devtools::install_github("hodgettsp/cesR")

library(cesR)

cesR::get_decon()

install.packages("tidyverse")
library(tidyverse)
```
# Data
```{r}
head(decon)
```

# Including Plots

```{r}
decon %>%
  ggplot(aes(x= education)) +
  geom_bar()+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5, hjust=1))+
  ggtitle("Education of Citizens in 2019 CES")+
  coord_flip()
```
The above ggplot shows a count of various responses to the education question in the 2019 Canadian Election study. We see a majority response among citizens having completed secondary/high school, Community college or Bachelor's Degree.  

```{r}
decon %>%
  ggplot(aes(x= employment)) +
  geom_bar()+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5, hjust=1))+
  ggtitle("Education of Citizens in 2019 CES")+
  coord_flip()
```

# Weaknesses and Next Steps

# References

- Stephenson, Laura B; Harell, Allison; Rubenson, Daniel; Loewen, Peter John, 2020, '2019 Canadian Election Study - Online Survey', https://doi.org/10.7910/DVN/DUS88V, Harvard Dataverse, V1
- Paul A.Hodgetts and Rohan Alexander (2020). cesR: Access the CES Datasets a
  Little Easier.. R package version 0.1.0


